An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-25 intro.tex
more changes

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable record of computations, especially computations whose results are destined for publication and/or re-use; images, like files, can then be shared \cite{Lampoudi}. 
However, the resulting image may be too big to share or distribute widely. An alternative light-weight form of virtualization is to encapsulate only the application software, along with all its necessary dependencies, into a self-contained package. The encapsulation is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}. However, the package is not longer an executable record of the computation and still needs an accompanying operating system for execution.

While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result. Often

Since reproducibility includes documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations so that they are easy to understand, install, or alter implicit dependencies that are part of computation is not effectively addressed, especially as dependencies and software components evolve or become deprecated. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. 
In this paper we examine the second approach. 
In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot~\cite{thain2005parrot}, CDE, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.

We do not claim our solution is the only way to preserve applications. Generally, there are two different approaches to preserve applications: measure the mess and force cleanliness. The first approach allows end users to construct the environment as desired, and then measures the dependencies. The latter one forces users to specify the execution environment for an application in a well organized way.
Our objective here is to preserve the mess as-is.

>>>>

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable record of computations, especially computations whose results are destined for publication and/or re-use; images, like files, can then be shared \cite{Lampoudi}. 
However, the resulting image may be too big to share or distribute widely. An alternative light-weight form of virtualization is to encapsulate only the application software, along with all its necessary dependencies, into a self-contained package. The encapsulation is achieved by OS-level sandboxing techniques that interpose application system calls, and copy the necessary dependencies (data, libraries, code, etc.) into a package, making it lighter weight than a VMI~\cite{guo2011cde}. However, the package is not longer an executable record of the computation and still needs an accompanying operating system for execution.

While both approaches provide mechanisms for encapsulating the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result. In general, in the absence of reproducible policy guidelines, such guarantees can be hard to provide. However, we can certainly improve upon the guarantees by \emph{preserving} the encapsulated computations in such a way that they are always reproducible. A preservation mechanism, if present, can make it easy to install images or packages, alter implicit dependencies that are part of computation as software components evolve or become deprecated, and finally provide  mechanisms for documentation that make computations easy to understand.

%Since reproducibility includes documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations so that they are easy to understand, install, or alter implicit dependencies that are part of computation is not effectively addressed, especially as dependencies and software components evolve or become deprecated.

There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. 
In this paper we examine the second approach.  
In particular, we consider the light-weight virtualization approaches, because, we believe that a combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers.  
A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot~\cite{thain2005parrot}, CDE, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.

We do not claim our solution is the only way to preserve applications. Broadly, there are two different approaches to preserve applications: force cleanliness or measure the mess. The first approach forces users to specify the execution environment for an application in a well organized way. In the latter one end users construct the environment as desired, and the complexity of the environment is measured in terms of its dependencies. 
Our objective here is to measure the mess as-is and then preserve it over time.
